---
title: "Where do I live next?"
author: "Vicki Lowe"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Install / load required packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load(httr, jsonlite)
```

## I need data

The Domain Group provides access to their agency, listing, and property data by [signing up](https://developer.domain.com.au/docs) for an account. I followed their [Getting Started](https://developer.domain.com.au/docs/read/Getting_Started) instructions and found out that I could get all the rental information available on [domain.com.au](domain.com.au).

My access token expired after 12 hours, so I automated the renewal process:
```{r get access to the Domain Group}
# Read in my Domain Group credentials: client_id and client_secret
source('api_keys_domain.R')

# Get latest access token
access.token.response <- GET(
  "https://developer.domain.com.au/io-docs/getoauth2accesstoken",
  query = list(
    apiId = 6611,
    auth_flow = "client_cred",
    client_id = client_id,
    client_secret = client_secret),
  verbose())
access.token <- content(access.token.response)$result$access_token
```

Now I can request the listing information that I want. Let's start with Pyrmont:
```{r use the listing API}
# Set up the request format to match https://developer.domain.com.au/io-docs
pyrmont.rentals <- POST(
  "https://api.domain.com.au/v1/listings/_search", 
  add_headers(
    Authorization = paste("Bearer", access.token), 
    "Content-Type" = "application/json"), 
          body = list(
            listingtype = "Rent", 
             locations = list(
               list(
                 state = "NSW",
                 suburb = "Pyrmont")),
            pageSize = 200),
          encode = "json", verbose())

# Check that the response is valid
# 2xx = success
# 4xx or 5xx = error
pyrmont.rentals$status_code

pyrmont.rentals.headers <- headers(pyrmont.rentals)
pyrmont.rentals.content <- content(pyrmont.rentals)

# Shifting to prettyprinted JSON to ease readability
pyrmont.rentals.json <- toJSON(content(pyrmont.rentals), pretty = TRUE)
# pyrmont.rentals.json

# How many properties are there?
length(pyrmont.rentals.content)
```